Distrivia: A Distributed Trivia Game

### 2011-03-25 papers/phase-zero/paper.tex
Fix spelling, add new image from sam to the paper, fix formatting.

\subsection{Clients}
The client will be pretty straightforward.
If you have never played Distrivia before, the game will prompt for the player to create a player name.
After which, it will allow the user to request to play a game.
Once the server has grouped 20 players together, the round will start and the screen will show the question followed by 4 selectable answers.
Once the user has selected their answer, they can hit the Submit button at the bottom to submit their answer for that question.
At that point, the player's answer is sent to the server, their new score along with their next question is sent back to the player.
At the bottom of the screen, the player will be able to select from thumbs up/thumbs down buttons if they particularly like or dislike a question.
This will be particularly useful if we have time to allow users to create their own questions to add the to the database.
Once a questions dislike ratio is too high, the question will no longer be asked.

@@

\subsection{Backend}
The server has four key layers involved.
First, there will be a load balancer that accepts all messages from the players.
It does not need to read the contents of the message, it simply distributes the message on to the most reliable server with the lowest load.
This ensures that if any of the servers were to go down, that the system would still run.
It also maintains highest speeds for server response.
The message is passed to a web server from the load balancer, which will read the contents of the message and respond appropriately.
These messages will be in the form of http messages.
The web server communicates directly with the database to perform whatever actions need to be done.
The third layer is represented by these synchronous databases that hold all the actual data for the software.
This would include round information, player information, and all the questions for the application.
The fourth and final layer would be some sort of master process that does the
actual synchronization between the databases so that they all contain redudant data for reliable communication.

\begin{center}
  \includegraphics[scale=0.3]{design-pictures/database.png}
\end{center}

\newpage
%
% The following two commands are all you need in the
% initial runs of your .tex file to
% produce the bibliography for the citations in your paper.
%/\bibliographystyle{abbrv}
%\bibliography{bibliography}  % sigproc.bib is the name of the Bibliography in this case
% You must have a proper ".bib" file
%  and remember to run:
% latex bibtex latex
% to resolve all references
%
% ACM needs 'a single self-contained file'!
%
%APPENDICES are optional
\balancecolumns
% That's all folks!
\end{document}

>>>>

%\subsection{Clients}
The client will be pretty straightforward.
If you have never played Distrivia before, the game will prompt for the player to create a player name.
After which, it will allow the user to request to play a game.
Once the server has grouped 20 players together, the round will start and the screen will show the question followed by 4 selectable answers.
Once the user has selected their answer, they can hit the Submit button at the bottom to submit their answer for that question.
At that point, the player's answer is sent to the server, their new score along with their next question is sent back to the player.
At the bottom of the screen, the player will be able to select from thumbs up/thumbs down buttons if they particularly like or dislike a question.
This will be particularly useful if we have time to allow users to create their own questions to add the to the database.
Once a questions dislike ratio is too high, the question will no longer be asked.

@@

%\subsection{Backend}
The server has four key layers involved.
First, there will be a load balancer that accepts all messages from the players.
It does not need to read the contents of the message, it simply distributes the message on to the most reliable server with the lowest load.
This ensures that if any of the servers were to go down, that the system would still run.
It also maintains highest speeds for server response.
The message is passed to a web server from the load balancer, which will read the contents of the message and respond appropriately.
These messages will be in the form of http messages.
The web server communicates directly with the database to perform whatever actions need to be done.
The third layer is represented by these synchronous databases that hold all the actual data for the software.
This would include round information, player information, and all the questions for the application.
Currently we are looking at using Riak for our database engine.
Riak has the unique ability to perform automatic master less replication and
synchronization between all nodes of a database cluster. With this architecture 
all back end nodes except for one could fail and our system would remain
operational.
\begin{center}
  \includegraphics[scale=0.35]{design-pictures/database2.png}
\end{center}

\newpage
%
% The following two commands are all you need in the
% initial runs of your .tex file to
% produce the bibliography for the citations in your paper.
%\bibliographystyle{abbrv}
%\bibliography{bibliography}  % sigproc.bib is the name of the Bibliography in this case
% You must have a proper ".bib" file
%  and remember to run:
% latex bibtex latex
% to resolve all references
%
% ACM needs 'a single self-contained file'!
%
%APPENDICES are optional
\balancecolumns
% That's all folks!
\end{document}
